Analysis for Project

### 2021-11-24 analysis/analysis.Rmd
Switch analysis.Rmd to robobook html output
I am using the rmdformats library to output results using the robobook format. This gives me nicer formatting and a dynamic table of contents to get around

---
title: "Analysis for Project"
output: 
  html_document: 
    fig_height: 6
    fig_width: 9
    toc: yes
    toc_depth: 4
---

@@

sapply(list("categorical, additive"=model_add_cat,
            "categorical, interaction"=model_inter_cat, 
            "continuous, additive"=model_add_cont, 
            "continuous, interaction"=model_inter_cont), 
       BIC) %>%
    enframe("model","BIC") %>%
  kbl()

>>>>

---
title: "Analysis for Project"
output: 
  rmdformats::robobook:
    highlight: tango
    toc_depth: 2
    fig_height: 6
    fig_width: 9
---

@@

sapply(list("categorical, additive"=model_add_cat,
            "categorical, interaction"=model_inter_cat, 
            "continuous, additive"=model_add_cont, 
            "continuous, interaction"=model_inter_cont), 
       BIC) %>%
    enframe("model","BIC") %>%
  kbl() %>%
  kable_styling(full_width=FALSE)
